Combining formal and distributional models of predicate semantics

### 2016-03-03 paper/paper.tex
A bit more work on the paper
Former-commit-id: d1ba10d3d7acfd0db4b1ed2ff812cf82cd01e264
Former-commit-id: d27feb8d09883d0e8b5101ff89ab7a5216e8f1be

The rest of this paper is organized as follows.  In \secref{background}, we
describe the relevant background necessary to understand the models we propose,
and we situate our model in the context of related work.  In \secref{method},
we give a formal description of our models of predicate semantics.  In
\secref{experiments}, we present experimental results on fill-in-the-blank
natural language query task.  Using web text linked to Freebase as our training
and test data, we show a 63\% relative improvement over prior work, giving a
new state-of-the-art result on this dataset.  In \secref{discussion}, we give a
detailed discussion of the benefits and drawbacks of the models we have
proposed.  We then conclude in \secref{conclusion}.

@@

\subsection{Open-vocabulary semantic parsing}

@@

Manaal's retrofitting semantic lexicons, Sebastian Riedel's ``Injecting Logical
Background Knowledge into Embeddings for Relation Extraction'', work on PRA and
KBC more generally\ldots

@@

@@

\section{Experiments}
\label{sec:experiments}

@@

>>>>

The rest of this paper is organized as follows.  In \secref{background}, we
describe the relevant background necessary to understand the models we propose,
and we situate our model in the context of related work.  In \secref{method},
we give a formal description of our models of predicate semantics.  In
\secref{evaluation}, we present experimental results on fill-in-the-blank
natural language query task.  Using web text linked to Freebase as our training
and test data, we show a 63\% relative improvement over prior work, giving a
new state-of-the-art result on this dataset.  In \secref{discussion}, we give a
detailed discussion of the benefits and drawbacks of the models we have
proposed.  We then conclude in \secref{conclusion}.

@@

\subsection{Open-vocabulary semantic parsing}
\label{sec:jayant-semparse}

@@

Some related work on including structured information in distributional
representations: Manaal's retrofitting semantic lexicons, Sebastian Riedel's
``Injecting Logical Background Knowledge into Embeddings for Relation
Extraction'', work on PRA and KBC more generally\ldots Also, the whole line of
work on knowledge base embeddings (RESCAL, TransE, etc.) is at least slightly
relevant here, as is PRA.  \mattnote{Actually write
this section}.

@@

\subsection{Adding SFE features to Jayant's models}
\label{sec:formal-and-distributional}

@@

\subsection{Finding relevant features for each predicate}
\label{sec:computing-pmi}

@@

\subsection{Improved logical forms}
\label{sec:better-lfs}

\section{Evaluation}
\label{sec:evaluation}

We evaluate our models of predicate semantics on a fill-in-the-blank natural
language query task.  Each test example is a natural language phrase containing
at least two Freebase entities, one of which is held out.  The system must
propose Freebase entities to fill in the blank left by the held out entity, and
the predicted entities are then judged manually for correctness.  We compare
our proposed models, which combine distributional and formal elements, with
distributional-only and formal-only baselines.

\subsection{Data}

We use the dataset introduced by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}, which
consists of the ClueWeb09 web
corpus\footnote{http://www.lemuproject.org/clueweb09.php} along with Google's
FACC entity linking of that corpus to
Freebase~\cite{gabrilovich-2013-clueweb-entity-linking}.  3 million webpages
from this corpus were processed with a CCG parser to produce logical forms, as
described in \secref{jayant-semparse}.  This produced 2.1m predicate instances
involving 142k entity pairs and 184k entities.  After removing
infrequently-seen predicates (seen fewer than 6 times), there were 25k
categories and 4.2k relations.\footnote{The differences in numbers reported
here versus those reported by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} are due to the
improved logical form generation, discussed in \secref{better-lfs}.}

\subsection{Methodology}

\subsection{Models}

\subsection{Results}
